A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-27 paper/ms.tex
update ms

Kepler\,1627Ab therefore provides an interesting extremum in the ages of the
Kepler planets, and opens multiple avenues for detailed
study.  In order of ascending difficulty, observing its
Doppler transit ($\Delta v_{\rm RM} \approx 20$\ms) with HIRES or the
upcoming KPF spectrograph could yield a measurement of its orbital
obliquity (CITEP,CITEP).  A transmission
spectrum focused on either hydrogen or helium absorption could yield
insight into its atmosphere, which is expected to be outflowing at a
rate of {\bf X.X}\,$M_\oplus\,{\rm yr}^{-1}$ (CITE).  Finally, the
most challenging measurement that may currently be in reach would be a
measurement of its mass, through either detailed timing analyses of
the Kepler data, or through a high-cadence multi-color radial velocity campaign.  The mass would yield constraints on both the planet's
composition (do the mini-Neptunes form with gaseous envelopes?), as
well as its initial entropy (``hot'' or ``cold''? CITE).

>>>>

Kepler\,1627Ab therefore provides an interesting extremum in the ages of the
Kepler planets, and opens multiple avenues for detailed
study.  In order of ascending difficulty, observing its
Doppler transit ($\Delta v_{\rm RM} \approx 20$\ms) with HIRES or the
upcoming KPF spectrograph could yield a measurement of its orbital
obliquity (CITEP,CITEP).  
(A simpler path to the same result might be to determine whether the
$\approx80\,{\rm ppm}$ residual apparent in our transit fit is caused
by gravity darkening.)
A transmission
spectrum focused on either hydrogen or helium absorption could yield
insight into its atmosphere, which is expected to be outflowing at a
rate of {\bf X.X}\,$M_\oplus\,{\rm yr}^{-1}$ (CITE).  Finally, the
most challenging measurement that may currently be in reach would be a
measurement of its mass, through either detailed timing analyses of
the Kepler data, or through a high-cadence multi-color radial velocity campaign.  The mass would yield constraints on both the planet's
composition (do the mini-Neptunes form with gaseous envelopes?), as
well as its initial entropy (``hot'' or ``cold''? CITE).
